---
title: "R Notebook"
output: html_notebook
---

After making some (hopefully final) changes, I re-ran the simulation and benchmarking analysis.

```{r include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
library(tidyverse)

source("sim_functions.R")

AAV_OTC_dir <- "../out/experiment1_OTC_chr1/AAV-OTC"
score_types <- c("shortest", "coords_mean", "coords_min", "midpoint")
OTC_conds_dir <-"../out/experiment1_OTC_chr1/OTC-condition-breakdown/"

```


# AAV and OTC integration

I simulated data as before - with an OTC and AAV condition - and compared the performance of various viral integration tools in various ways.  I simulated integrations into either chromosome 1, or all of hg38.  I used hg38 for analysis in the intergration tools.

For simulation, we had the following conditions:
```{r include=FALSE}
sim_conds <- importSimulationConditions(AAV_OTC_dir)
```

```{r}
sim_conds
```


On the analysis side, we had the following analysis conditions
```{r include=FALSE}
analysis_conds <- importAnalysisConditions(AAV_OTC_dir) %>% 
  select(-one_of("adapter_1", "adapter_2"))
```

```{r}
analysis_conds 
```

## Jaccard


```{r include=FALSE}
jac <- importJaccardExperiment(AAV_OTC_dir) %>% 
  mutate(pad = as.integer(str_extract(sim_file, "(?<=pad)\\d+"))) %>% 
  mutate(analysis_tool = str_replace(analysis_tool, "analysis", "isling")) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, "analysis", "isling")) %>% 
  mutate(analysis_condition_short = str_replace(analysis_condition_short, "analysis", "isling"))

jac <- jac %>% 
  filter(!is.na(host_name))

unique(jac$condition)
```


```{r}
jac %>% 
  select(host_name, virus_name, analysis_tool, replicate, pad, jaccard, intersection, union, n_intersections, experiment, analysis_condition, analysis_condition_short)
```


```{r fig.height=10, fig.width=10}
plotlist <- list()
for (p in unique(jac$pad)) {
  plotlist[[glue("{p}")]] <- jac %>% 
    filter(pad == p) %>% 
    ggplot(aes(x = analysis_condition_short, y = jaccard)) +
    geom_boxplot() +
    geom_point() +
    facet_wrap(experiment~host_name, scales="free") +
    ggtitle(glue("padding {p}")) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
cowplot::plot_grid(plotlist=plotlist)
```


## sim-to-found distances
```{r include=FALSE}

#import distances from each found integration to nearest simulated integration
found_scores <- importNearestSimToFound(AAV_OTC_dir) 


# only use postprocessed data from our pipeline
found_scores <- found_scores %>% 
  filter(case_when(
    !str_detect(analysis_condition, "pipeline") ~ TRUE,
    post ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling')) %>% 
  mutate(tool = str_replace(analysis_condition, "\\d+", "")) %>% 
  filter(experiment == "AAV" | experiment == "OTC")

# import distances from each simulated integration to the nearest found integration
sim_scores <- importNearestFoundToSim(AAV_OTC_dir) 

sim_scores <- sim_scores%>% 
  filter(case_when(
    !str_detect(analysis_condition, "pipeline") ~ TRUE,
    post ~ TRUE,
    TRUE ~ FALSE
  )) %>%  
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling')) %>% 
  mutate(tool = str_replace(analysis_condition, "\\d+", "")) %>% 
  filter(experiment == "AAV" | experiment == "OTC")

```

```{r fig.height=10, fig.width=10}
dist_add <- 0.5
plotlist <- list()
plot_cols <- paste0("d_", score_types)
for (s in plot_cols) {
  plotlist[[s]] <- sim_scores %>% 
   mutate(s := !!ensym(s)+dist_add) %>% 
   ggplot(aes(x = s, color = analysis_condition)) +
    geom_freqpoly(bins = 100) +
    scale_x_log10() +
    facet_wrap(experiment~condition, scales="free_y") +
    ggtitle(s) +
    xlab("distance") +
    theme(legend.position = "none")
}
p <- cowplot::plot_grid(plotlist=plotlist)
legend <- cowplot::get_legend(plotlist[[s]] + theme(legend.position = "bottom"))
cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(1, 0.1))
```

## found-to-sim distances

```{r fig.height=10, fig.width=10}
dist_add <- 0.5
plotlist <- list()
for (s in plot_cols) {
  plotlist[[s]] <- found_scores %>% 
   mutate(s := !!ensym(s)+dist_add) %>% 
   ggplot(aes(x = s, color = analysis_condition)) +
    geom_freqpoly(bins = 100) +
    scale_x_log10() +
    facet_wrap(experiment~condition, scales="free_y") +
    ggtitle(s) +
    xlab("distance") +
    theme(legend.position = "none")
}
p <- cowplot::plot_grid(plotlist=plotlist)
legend <- cowplot::get_legend(plotlist[[s]] + theme(legend.position = "bottom"))
cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(1, 0.1))
```




```{r}
score_dists <- function(dists, group_cols, above_threshold = "fp", score_col = "d_coords_mean", threshold = 5) {
  print(glue("checking column {score_col} with threshold {threshold}"))
  return(dists %>% 
           mutate(score = case_when(
             !!ensym(score_col) == -1 ~ above_threshold,
             !!ensym(score_col) > threshold ~ above_threshold,
             !!ensym(score_col) <= threshold ~ "tp",
             TRUE ~ as.character(NA)
           )) %>% 
           group_by(across(one_of(c(group_cols, "score")))) %>% 
           tally() %>% 
           mutate(window = threshold) %>% 
           mutate(score_type = score_col) %>% 
           ungroup())
  
}

all_scores <- function(found_dists, sim_dists, group_cols, threshold, score_col) {
  
  found <- score_dists(found_dists, group_cols, above_threshold ="fp", score_col, threshold) %>% 
    filter(score == "fp")
  sim <- score_dists(sim_dists, group_cols, above_threshold ="fn", score_col, threshold)
  
  
  return(
    bind_rows(found, sim) %>% 
           pivot_wider(names_from = score, values_from = n, values_fill = 0) %>% 
      ungroup() %>% 
      rowwise() %>% 
      mutate(PPV = tp / (tp + fp)) %>% 
      mutate(TPR = tp / (tp + fn)) %>% 
      ungroup()
         )
}


#all_scores(found_scores, sim_scores, group_cols = group_cols, threshold = 5, score_col = "d_midpoint")  %>%
# arrange(experiment, condition, replicate)
```


```{r include=FALSE}
group_cols<- c("unique", "analysis_condition", "experiment", "condition", "replicate",  "analysis_host", "analysis_virus", "post", "tool")

dists = c(0, 2, 5, 10, 30, 60, 100)


int_scores <- tibble()

for (s in plot_cols) {
  
  for (t in dists) {
    
    int_scores <- bind_rows(
      int_scores, all_scores(found_scores, sim_scores, 
                             group_cols = group_cols, threshold = t, score_col = s) 
    )
  }
  
}

```


```{r}
int_scores %>% 
  select(analysis_host, analysis_virus, tool, window, score_type, replicate, PPV, TPR, tp:fp, experiment)
```


```{r fig.height=10, fig.width=10}
plotlist <- list()
for (w in unique(int_scores$window)) {
  plotlist[[glue("{w}")]] <- int_scores %>% 
    filter(window == w) %>% 
    ggplot(aes(x = PPV, y = TPR, color = analysis_condition, shape = score_type)) +
    geom_point() +
    xlim(0, 1) +
    ylim(0, 1) +
    facet_wrap(condition~analysis_virus) +
    theme(legend.position = "none") +
    ggtitle(glue("dist threshold: {w}"))
}

legend <- cowplot::get_legend(plotlist[["0"]] + theme(legend.position = "bottom"))
p <- cowplot::plot_grid(plotlist=plotlist)
cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(1, 0.1))
```

```{r fig.height=8, fig.width=8}
int_scores %>% 
    filter(window == 60) %>% 
    filter(condition == "cond0") %>% 
    ggplot(aes(x = PPV, y = TPR, color = analysis_condition, shape = score_type)) +
    geom_point() +
    xlim(0, 1) +
    ylim(0, 1) +
    facet_grid(score_type~analysis_virus) +
    theme(legend.position = "bottom") +
    ggtitle(glue("dist threshold: {100}"))
```


```{r}
int_scores %>% 
    filter(window == 5) %>% 
    filter(condition == "cond0") %>% 
  filter(score_type == "d_shortest") %>% 
  filter(ifelse(str_detect(analysis_condition, 'isling'), analysis_condition=='isling2', TRUE)) %>% 
    ggplot(aes(x = PPV, y = TPR, color = analysis_condition, shape = score_type)) +
    geom_point() +
    xlim(0, 1) +
    ylim(0, 1) +
    facet_wrap(condition~analysis_virus) +
    theme(legend.position = "bottom") +
    ggtitle(glue("dist threshold: {5}"))
```


```{r}
int_scores %>% 
    filter(window == 60) %>% 
    filter(condition == "cond0") %>% 
  filter(score_type == "d_shortest") %>% 
  filter(ifelse(str_detect(analysis_condition, 'isling'), analysis_condition=='isling2', TRUE)) %>% 
    ggplot(aes(x = PPV, y = TPR, color = analysis_condition, shape = score_type)) +
    geom_point() +
    xlim(0, 1) +
    ylim(0, 1) +
    facet_wrap(condition~analysis_virus) +
    theme(legend.position = "bottom") +
    ggtitle(glue("dist threshold: {100}"))
```



```{r}
scoring_dist <- 5
jaccard_pad <- 0
dist_add <- 0.5
plot_score_type <- "d_shortest"
analysis_condition_plot <- "isling1"
tool_order <- c("isling", "Polyidus", "Seeksv", "ViFi", "VSeq-Toolkit")
condition_plot <- "cond0"
num_y_breaks <- 2

jac_plot <- jac %>% 
  filter(case_when(
    str_detect(analysis_condition_short, "analysis|pipeline|isling") ~ analysis_condition_short == analysis_condition_plot,
    TRUE ~ TRUE
  )) %>% 
  filter(pad == jaccard_pad) %>% 
  filter(condition == condition_plot) %>% 
  mutate(tool = case_when(
    analysis_tool == "polyidus" ~ "Polyidus",
    analysis_tool == "seeksv" ~ "Seeksv",
    analysis_tool == "vifi" ~ "ViFi",
    analysis_tool == "vseq-toolkit" ~ "VSeq-Toolkit",
    TRUE ~ analysis_tool
  )) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  mutate(experiment = str_replace(experiment, "-harder", ""))

jac_plots <- list()
for (e in unique(jac_plot$experiment)) {
  jac_plots[[e]] <- jac_plot %>% 
    filter(experiment == e) %>% 
    ggplot(aes(x = tool, y = jaccard, color = tool)) +
    geom_boxplot(width=0.5) +
    theme_classic() +
    theme(axis.text.x = element_blank(),
          legend.position = "none")  +
    ylab("Jaccard") +
    xlab("Tool")
}

print(jac_plots[[e]])

sim_plot <- sim_scores %>% 
  filter(condition == condition_plot) %>% 
filter(case_when(
    str_detect(analysis_condition, "analysis|pipeline|isling") ~ analysis_condition == analysis_condition_plot,
    TRUE ~ TRUE
  )) %>% 
  mutate(tool = case_when(
    tool == "polyidus" ~ "Polyidus",
    tool == "seeksv" ~ "Seeksv",
    tool == "vifi" ~ "ViFi",
    tool == "vseq-toolkit" ~ "VSeq-Toolkit",
    TRUE ~ tool
  ))  %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  mutate(experiment = str_replace(experiment, "-harder", ""))

sim_plots <- list()
for (e in unique(sim_plot$experiment)) {
  sim_plots[[e]] <- sim_plot %>% 
    filter(experiment == e) %>%
    mutate(plot_score_type := !!ensym(plot_score_type) + dist_add) %>% 
    ggplot(aes(x = !!ensym(plot_score_type), color = tool)) +
    geom_freqpoly(bins = 100) +
    geom_vline(xintercept = scoring_dist) +
    theme_classic() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          strip.background = element_blank(),
          strip.text.y = element_blank(),
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_x_log10() +
    facet_grid(rows = vars(tool)) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = num_y_breaks)) +
    ylab("Count")
}
print(sim_plots[[e]])

found_plot <- found_scores %>% 
  filter(condition == condition_plot) %>% 
  filter(case_when(
    str_detect(analysis_condition, "analysis|pipeline|isling") ~ analysis_condition == analysis_condition_plot,
    TRUE ~ TRUE
  )) %>% 
  mutate(tool = case_when(
    tool == "polyidus" ~ "Polyidus",
    tool == "seeksv" ~ "Seeksv",
    tool == "vifi" ~ "ViFi",
    tool == "vseq-toolkit" ~ "VSeq-Toolkit",
    TRUE ~ tool
  ))  %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  mutate(experiment = str_replace(experiment, "-harder", ""))

found_plots <- list()
for (e in unique(found_plot$experiment)) {
  found_plots[[e]] <- found_plot %>% 
    filter(experiment == e) %>% 
    mutate(plot_score_type := !!ensym(plot_score_type) + dist_add) %>% 
    ggplot(aes(x = !!ensym(plot_score_type), color = tool)) +
    geom_freqpoly(bins = 100) +
    geom_vline(xintercept = scoring_dist) +
    theme_classic() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          strip.background = element_blank(),
          strip.text.y = element_blank(),
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_x_log10() +
    facet_grid(rows = vars(tool)) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = num_y_breaks)) +
    ylab("Count")
}
print(found_plots[[e]])

scores_plot <- int_scores %>% 
  filter(condition == condition_plot) %>% 
  filter(window == scoring_dist) %>% 
  filter(score_type == plot_score_type) %>% 
  filter(case_when(
    str_detect(analysis_condition, "analysis|pipeline|isling") ~ analysis_condition == analysis_condition_plot,
    TRUE ~ TRUE
  )) %>% 
    mutate(tool = case_when(
    tool == "polyidus" ~ "Polyidus",
    tool == "seeksv" ~ "Seeksv",
    tool == "vifi" ~ "ViFi",
    tool == "vseq-toolkit" ~ "VSeq-Toolkit",
    TRUE ~ tool
  )) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  mutate(experiment = str_replace(experiment, "-harder", "")) 

scores_plots <- list()
for (e in unique(scores_plot$experiment)) {
  scores_plots[[e]] <- scores_plot %>% 
    filter(experiment == e) %>% 
    ggplot(aes(x = PPV, y = TPR, color = tool)) +
    geom_point() +
    theme_classic() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    xlim(0, 1) +
    ylim(0, 1)
  
}
print(scores_plots[[e]])

experiments <- unique(scores_plot$experiment)

plotlist <- list()
for (e in experiments) {
  plotlist[[glue("jac_{e}")]] <- jac_plots[[e]]
  plotlist[[glue("sim_{e}")]] <- sim_plots[[e]]
  plotlist[[glue("found_{e}")]] <- found_plots[[e]]
  plotlist[[glue("score_{e}")]] <- scores_plots[[e]]
}

p <- cowplot::plot_grid(plotlist=plotlist, nrow = length(experiments), labels="AUTO")
legend <- cowplot::get_legend(plotlist[[glue("score_{e}")]] + theme(legend.position = "bottom"))
p2 <- cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(1, 0.05))
cowplot::save_plot("plots/figure1.5dist.pdf", p2)

```



```{r}
print(p2)
```


Make some tables so we can pull some numbers for the text

## Jaccard

```{r}
jac_table <- jac_plot %>% 
  select(experiment, tool, condition, replicate,jaccard, intersection, union, host_name, virus_name, analysis_host, analysis_virus, analysis_condition)

jac_table

jac_table %>% 
  write_tsv("tables/AAV_OTC_jaccard.tsv")
```

```{r}
jac_summary <- jac_plot %>% 
  group_by(experiment, tool, condition, host_name, virus_name, analysis_host, analysis_virus, analysis_condition) %>% 
  summarise(
    n = n(),
    mean_jac = mean(jaccard),
    sd_jac = sd(jaccard),
    sem_jac = sd(jaccard)/sqrt(n()),
    mean_intersect = mean(intersection),
    sd_intersect = sd(intersection),
    sem_intersect = sd(intersection)/sqrt(n()),
    mean_union = mean(union),
    sd_union = sd(union),
    sem_union = sd(union)/sqrt(n())
  ) 

jac_summary

jac_summary %>% 
  write_tsv("tables/AAV_OTC_jaccard_summary.tsv")
```


## TPR, PPV

```{r}
scores_table <- scores_plot %>% 
  select(experiment, tool, replicate, fp:TPR, window, condition, analysis_host, analysis_virus, analysis_condition)

scores_table

jac_table %>% 
  write_tsv("tables/AAV_OTC_scores.tsv")

```


```{r}
scores_summary <- scores_plot %>% 
  group_by(experiment, tool, window, condition, analysis_host, analysis_virus, analysis_condition) %>% 
  summarise(
    n = n(),
    mean_TPR = mean(TPR),
    sd_TPR = sd(TPR),
    sem_TPR = sd(TPR)/sqrt(n()),
    mean_PPV = mean(PPV),
    sd_PPV = sd(PPV),
    sem_PPV = sd(PPV)/sqrt(n())
  )

scores_summary

scores_summary %>% 
  write_tsv("tables/AAV_OTC_scores_summary.tsv")
```

```{r}
# we also want to know the lengths of output intervals to show that they're really long for ViFi

found_scores %>% 
  mutate(interval_len = stop-start) %>% 
  group_by(experiment, analysis_condition, condition, analysis_host, analysis_virus, tool) %>% 
  summarise(mean = mean(interval_len),
            sd = sd(interval_len),
            n = n()) %>% 
  write_tsv("tables/AAV_OTC_lengths_summary.tsv")
  


```



# Fold-coverage and chromosome

Within the OTC condition, I also explored the effect of increasing fold coverage and changing the host chromsome.

For this experiment I tried two different isling conditions - one had a minimum mapq of 20, and the other of 30.

## Jaccard

First looking at the effect of fold coverage and host chromosome on the jaccard statistic.

```{r include=FALSE}
jac <- importJaccardExperiment(OTC_conds_dir) %>% 
  mutate(pad = as.integer(str_extract(sim_file, "(?<=pad)\\d+"))) %>% 
  mutate(analysis_tool = str_replace(analysis_tool, "analysis", "isling"))

jac <- jac %>% 
  filter(pad != 2)

jac
```

```{r}
jac %>% 
  group_by(condition, fcov, analysis_tool, analysis_condition, pad, host_name) %>% 
  summarise(n = n(),
            jac_mean = mean(jaccard),
            jac_sd = sd(jaccard)) %>% 
  ggplot(aes(x = fcov, y = jac_mean, color = analysis_condition)) +
  geom_point() +
  geom_line() +
  facet_grid(rows = vars(host_name), cols = vars(pad)) +
  scale_x_log10()
```



## Scoring

We can also look at the effect on the positive predictive value and true positive rate


```{r include=FALSE}

#import distances from each found integration to nearest simulated integration
int_scores <- importIntScoreExperiment(OTC_conds_dir)

int_scores <- int_scores %>% 
  mutate(tool = str_replace(tool.x, "pipeline", "isling")) %>% 
  mutate(tool = str_replace(tool, "seeksv", "Seeksv")) %>% 
  mutate(tool = str_replace(tool, "polyidus", "Polyidus")) %>% 
  mutate(tool = str_replace(tool, "vifi", "ViFi")) %>% 
  mutate(tool = str_replace(tool, "vseq_toolkit", "VSeq-Toolkit"))

int_scores
```


```{r}
int_scores %>% 
  filter(is.na(analysis_condition))
```


```{r}
int_scores %>% 
  filter(window == 5) %>% 
  filter(coords_score_type == "coords_mean") %>% 
  group_by(fcov, analysis_condition, host_name, condition, window, coords_score_type) %>% 
  summarise(n = n(),
            mean_TPR = mean(TPR),
            sem_TPR = sd(TPR)/sqrt(n),
            min_TPR = mean_TPR - sem_TPR,
            max_TPR = mean_TPR + sem_TPR
            ) %>% 
  ggplot(aes(x = fcov, y = mean_TPR, color = analysis_condition, group=analysis_condition)) +
  geom_point() +
  geom_line() +
  geom_linerange(aes(ymin = min_TPR, ymax = max_TPR)) +
  facet_wrap(~host_name) +
  scale_x_log10()
```


```{r}
int_scores %>% 
  filter(window == 5) %>% 
  filter(coords_score_type == "shortest") %>% 
  group_by(fcov, analysis_condition, host_name, condition, window, coords_score_type) %>% 
  summarise(n = n(),
            mean_TPR = mean(TPR),
            sem_TPR = sd(TPR)/sqrt(n),
            min_TPR = mean_TPR - sem_TPR,
            max_TPR = mean_TPR + sem_TPR
            ) %>% 
  ggplot(aes(x = fcov, y = mean_TPR, color = analysis_condition, group=analysis_condition)) +
  geom_point() +
  geom_line() +
  geom_linerange(aes(ymin = min_TPR, ymax = max_TPR)) +
  facet_wrap(~host_name) +
  scale_x_log10()
```


```{r}
int_scores %>% 
  filter(window == 60) %>% 
  filter(coords_score_type == "shortest") %>% 
  group_by(fcov, analysis_condition, host_name, condition, window, coords_score_type) %>% 
  summarise(n = n(),
            mean_PPV = mean(PPV),
            sem_PPV = sd(PPV)/sqrt(n),
            min_PPV = mean_PPV - sem_PPV,
            max_PPV = mean_PPV + sem_PPV
            ) %>% 
  ggplot(aes(x = fcov, y = mean_PPV, color = analysis_condition, group=analysis_condition)) +
  geom_point() +
  geom_line() +
  geom_linerange(aes(ymin = min_PPV, ymax = max_PPV)) +
  facet_wrap(~host_name) +
  scale_x_log10()
```


## Figure 2

If we combine the jaccard, PPV and TPR, we get the following:

```{r include=FALSE}



makeFigue2 <- function(isling_condition, plot_score_type, scoring_dist) {
  
  jaccard_pad <- 0
  
  
jac_summary <- jac %>% 
  filter(pad == jaccard_pad) %>% 
  filter(case_when(
    str_detect(analysis_condition, "analysis") ~ str_detect(analysis_condition, isling_condition),
    TRUE ~ TRUE
  )) %>% 
  mutate(analysis_tool = case_when(
    analysis_tool == "polyidus" ~ "Polyidus",
    analysis_tool == "seeksv" ~ "Seeksv",
    analysis_tool == "vifi" ~ "ViFi",
    analysis_tool == "vseq-toolkit" ~ "VSeq-Toolkit",
    TRUE ~ analysis_tool
  )) %>% 
  mutate(analysis_tool = as.factor(analysis_tool)) %>% 
  mutate(analysis_tool = forcats::fct_relevel(analysis_tool, tool_order))  %>% 
  group_by(condition, fcov, analysis_tool, analysis_condition, pad, host_name) %>% 
  summarise(n = n(),
            jac_mean = mean(jaccard),
            jac_sem = sd(jaccard)/sqrt(n),
            jac_min = jac_mean - jac_sem,
            jac_max = jac_mean + jac_sem) 

jac_plot <- jac_summary %>% 
  ggplot(aes(x = fcov, y = jac_mean, color = analysis_tool)) +
  geom_point() +
  geom_line() +
  geom_linerange(aes(ymin = jac_min, ymax = jac_max)) +
  facet_grid(cols = vars(host_name)) +
  scale_x_log10() +
  theme_classic() +
  theme(legend.position = "none",
          axis.title.x = element_blank(),
          strip.background = element_blank(),
          strip.text.y = element_blank()) +
    ylim(0, 1) +
  ylab("Jaccard")


PPV_summary <- int_scores %>% 
  filter(window == scoring_dist) %>% 
  filter(coords_score_type == plot_score_type) %>% 
  filter(case_when(
    str_detect(unique.x, "analysis") ~ str_detect(unique.x, isling_condition),
    TRUE ~ TRUE
  )) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  group_by(condition, fcov, tool, unique.x, host_name) %>% 
  summarise(n = n(),
            PPV_mean = mean(PPV),
            PPV_sem = sd(PPV)/sqrt(n),
            PPV_min = PPV_mean - PPV_sem,
            PPV_max = PPV_mean + PPV_sem) 

PPV_plot <- PPV_summary %>% 
  ggplot(aes(x = fcov, y = PPV_mean, color = tool)) +
  geom_point() +
  geom_line() +
  geom_linerange(aes(ymin = PPV_min, ymax = PPV_max)) +
  facet_grid(cols = vars(host_name)) +
  scale_x_log10() +
  theme_classic() +
  theme(legend.position = "none",
          axis.title.x = element_blank(),
          strip.background = element_blank(),
          strip.text.y = element_blank(),
          strip.text.x = element_blank()) +
    ylim(0, 1) +
  ylab("PPV")


TPR_summary <- int_scores %>% 
  filter(window == scoring_dist) %>% 
  filter(coords_score_type == plot_score_type) %>% 
  filter(case_when(
    str_detect(unique.x, "analysis") ~ str_detect(unique.x, isling_condition),
    TRUE ~ TRUE
  )) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  group_by(condition, fcov, tool, unique.x, host_name) %>% 
  summarise(n = n(),
            TPR_mean = mean(TPR),
            TPR_sem = sd(TPR)/sqrt(n),
            TPR_min = TPR_mean - TPR_sem,
            TPR_max = TPR_mean + TPR_sem) 

TPR_plot <- TPR_summary %>% 
  ggplot(aes(x = fcov, y = TPR_mean, color = tool)) +
  geom_point() +
  geom_line() +
  geom_linerange(aes(ymin = TPR_min, ymax = TPR_max)) +
  facet_grid(cols = vars(host_name)) +
  scale_x_log10() +
  theme_classic() +
  theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.y = element_blank(),
          strip.text.x = element_blank()) +
    ylim(0, 1) +
  ylab("TPR") +
  xlab("Fold coverage")


p <- cowplot::plot_grid(jac_plot, PPV_plot, TPR_plot, labels="AUTO", ncol = 1)
legend <- cowplot::get_legend(jac_plot + theme(legend.position = "bottom"))
p2 <- cowplot::plot_grid(p, legend, ncol = 1, rel_heights = c(1, 0.05))
print(p2)
cowplot::save_plot(glue::glue("plots/figure2.{scoring_dist}dist.pdf"), p2)

return(list(p2, jac_summary, PPV_summary, TPR_summary))

  
}



p2 <- makeFigue2("analysis1|isling1", "shortest", 60)

```

```{r}
print(p2[[1]])
```

```{r}
p2 <- makeFigue2("analysis1|isling1", "shortest", 5)
print(p2[[1]])

p2[[2]] %>% 
  write_tsv("tables/OTC_condions_jaccard_5bp.tsv")
p2[[3]] %>% 
  write_tsv("tables/OTC_condions_PPV_5bp.tsv")
p2[[4]] %>% 
  write_tsv("tables/OTC_condions_TPR_5bp.tsv")
```


Check one of the results at 100X coverage to see what some of the false positives are - my guess is that they're just discordant pairs with a long fragment length

```{r}

high_fcov_ground_truth <- read_tsv('../out/experiment1_OTC_chr1/OTC-condition-breakdown/chr-fcov/sim_ints/cond27.rep0.int-info.annotated.tsv')


high_fcov_ground_truth
```


```{r}

high_fcov_found <- read_tsv('../out/experiment1_OTC_chr1/OTC-condition-breakdown/chr-fcov/scored_ints/chr-fcov_analysis1.cond27.rep0.hg38.OTC.post.found-results.tsv')

high_fcov_found %>% 
  filter(d_shortest > 5)

high_fcov_found %>% 
  filter(d_shortest > 5)

```

Most of these distances are short.   Maybe just make a table with the median distance for each contition/tool.  This is likely becaues of discordant pairs - can also make a table with how many output integrations have same read ID as a simulated integration.  First do the median thing.

```{r include=FALSE}

#import distances from each found integration to nearest simulated integration
found_scores <- importNearestSimToFound(OTC_conds_dir) 


# only use postprocessed data from our pipeline
found_scores <- found_scores %>% 
  filter(case_when(
    !str_detect(analysis_condition, "pipeline") ~ TRUE,
    post ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling')) %>% 
  mutate(tool = str_replace(analysis_condition, "\\d+", "")) 

# import distances from each simulated integration to the nearest found integration
sim_scores <- importNearestFoundToSim(OTC_conds_dir) 

sim_scores <- sim_scores%>% 
  filter(case_when(
    !str_detect(analysis_condition, "pipeline") ~ TRUE,
    post ~ TRUE,
    TRUE ~ FALSE
  )) %>%  
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling')) %>% 
  mutate(tool = str_replace(analysis_condition, "\\d+", "")) 

```



```{r}
found_scores_summary <- found_scores %>% 
  group_by(unique, analysis_condition, experiment, condition, tool) %>% 
  summarise(
    mean_found_to_sim = mean(d_shortest),
    median_found_to_sim = median(d_shortest),
    sd_found_to_sim = sd(d_shortest)
  )

sim_scores_summary <- sim_scores %>% 
    group_by(unique, analysis_condition, experiment, condition, tool) %>% 
   summarise(
    mean_sim_to_found = mean(d_shortest),
    median_sim_to_found = median(d_shortest),
    sd_sim_to_found = sd(d_shortest)
  ) 

dist_summary <- left_join(found_scores_summary, sim_scores_summary, by=c("analysis_condition", "unique", "experiment", "condition", "tool"))

dist_summary
```


```{r}

read_id_scoring <- compareAllIslingOutputSim(AAV_OTC_dir) %>% 
  select(-data)


write_tsv(read_id_scoring, "tables/read-id-scoring_AAV-OTC.tsv")

read_id_summary <- read_id_scoring %>% 
  group_by(experiment, analysis_condition, sim_experiemnt, condition, host_name, virus_name, fcov) %>% 
  summarise(
    mean_PPV = mean(PPV),
    sd_PPV = sd(PPV),
    sem_PPV = sd_PPV/sqrt(n()),
    n = n()
  )

read_id_summary

read_id_summary %>% 
  write_tsv("tables/read-id-summary_AAV-OTC.tsv")

read_id_scoring <- compareAllIslingOutputSim(OTC_conds_dir) %>% 
  select(-data)

write_tsv(read_id_scoring, "tables/read-id-scoring_OTC-conds.tsv")

read_id_summary <- read_id_scoring %>% 
  group_by(experiment, analysis_condition, sim_experiemnt, condition, host_name, virus_name, fcov) %>% 
  summarise(
    mean_PPV = mean(PPV),
    sd_PPV = sd(PPV),
    sem_PPV = sd_PPV/sqrt(n()),
    n = n()
  )

read_id_summary

read_id_summary %>% 
  write_tsv("tables/read-id-summary_OTC-conds.tsv")

```


