---
title: "Paper figures: runtime"
output: html_notebook
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F)
library(tidyverse)
```


Re-ran isling runtime benchmarking after changing to python implmentation of finding integrations.


Results:

# Runtime

I also looked at the runtime as I changed to variables: viral load and fold coverage

```{r include=FALSE}
results_dir <- "/datasets/work/hb-viralint/work/simulations/intvi_simulation-experiments/out/experiment2_time/"
experiments <- c("coverage", 'viral_load')

files <- list.files(results_dir, recursive = TRUE, pattern="_runtime.tsv")

files <- files[ basename(dirname(files)) %in% experiments]

files <- files[dirname(dirname(files)) == "."]


coltypes <- cols(
  tool = col_character(),
  dataset = col_character(),
  sample = col_character(),
  replicate = col_double(),
  exit_value = col_double(),
  user_time = col_double(),
  system_time = col_double(),
  elapsed_time = col_character(),
  CPU = col_character(),
  shared_text = col_double(),
  unshared_data = col_double(),
  max_rss = col_double(),
  fs_inputs = col_double(),
  fs_outputs = col_double(),
  major_page_faults = col_double(),
  minor_page_faults = col_double(),
  swaps = col_double(),
  command = col_character()
)

times <- tibble(
  filename = file.path(results_dir, files),
  experiment = dirname(files),
  data = map(filename, ~read_tsv(., col_types=coltypes))
) %>% 
  unnest(data) %>% 
  mutate(duration_elapsed_time = case_when(
    str_detect(elapsed_time, "\\d{0,2}:\\d{2}\\.\\d{2}") ~ lubridate::as.duration(lubridate::ms(elapsed_time)),
    str_detect(elapsed_time, "\\d{0,2}:\\d{2}\\:\\d{2}") ~ lubridate::as.duration(lubridate::hms(elapsed_time)),
    TRUE ~ lubridate::as.duration(NA)
  )) %>% 
  rename(time_rep = replicate)

# add simulation conditions
conds <- importSimulationConditions(results_dir)

times <- left_join(times, conds, by=c("experiment", "sample")) %>% 
  mutate(tool = str_replace(tool, "polyidus", "Polyidus")) %>% 
  mutate(tool = str_replace(tool, "seeksv", "Seeksv")) %>% 
  mutate(tool = str_replace(tool, "vifi", "ViFi")) %>% 
  mutate(tool = str_replace(tool, "vseq-toolkit", "VSeq-Toolkit"))  
```


```{r}
times <- times %>% 
  mutate(base_filename = basename(filename)) %>% 
  filter(base_filename %in% c( "coverage_runtime.tsv", "viral_load_runtime.tsv"))

```

First, check the exit values for each run, for each tool

```{r}
# how many times does each exit value occur?
times %>% 
  group_by(tool, exit_value) %>% 
  summarise(n = n())
```



Also check the number of replicates for each experiment, sample and tool - should be 3.

```{r}
times %>% 
  group_by(experiment, sample, tool) %>% 
  summarise(n = n())
```




Are there any that aren't 3?

```{r}
times %>% 
  group_by(experiment, sample, tool) %>% 
  summarise(n = n()) %>% 
  filter(n != 3)
```



## Runtime

Plotting the runtime ('elapsed time'):

```{r }

times %>% 
  mutate(tool = as.factor(tool)) %>% 
  ggplot(aes(x = condition, y = duration_elapsed_time, color=tool)) +
  geom_boxplot() +  
  facet_grid(rows = vars(experiment), scales = 'free') +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_discrete(name='tool')
```

What about user + sys time

```{r}
times <- times %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(user_sys_time = user_time + system_time)  %>% 
  ungroup()

times %>% 
  mutate(tool = as.factor(tool)) %>% 
  ggplot(aes(x = condition, y = user_sys_time, color=tool)) +
  geom_boxplot() +  
  facet_grid(rows = vars(experiment), scales = 'free') +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_discrete(name='tool')


```


## Figure 3

If we look at user + system time:

```{r}
tool_order <- c("isling", "Polyidus", "Seeksv", "ViFi", "VSeq-Toolkit")

viral_load <- times %>% 
  filter(experiment == "viral_load") %>% 
  mutate(int_num = as_factor(int_num)) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  group_by(int_num, epi_num, tool) %>% 
  summarise(n = n(),
            mean_time = mean(user_sys_time),
            sem_time = sd(user_sys_time)/sqrt(n),
            min = mean_time - sem_time,
            max = mean_time + sem_time) %>% 
  ungroup() %>% 
   ggplot(aes(x = int_num, y = mean_time, color=tool, group = tool)) +
  geom_point()  +
  geom_line() +
  geom_linerange(aes(ymin = min, ymax = max)) +
  facet_wrap(vars(epi_num)) +
  theme_classic()  + 
  theme(
    strip.background = element_blank(),
    strip.text.y = element_blank(),
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    #    axis.title.y = element_blank(),
  )  +
  xlab("Number of integrations") +
  ylab("Runtime (s)") +
  scale_y_log10()


#print(viral_load + theme(legend.position = "bottom"))

coverage <- times %>% 
  filter(experiment == "coverage") %>% 
  mutate(fcov = as.factor(fcov)) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  group_by(fcov, tool) %>% 
  summarise(n = n(),
            mean_time = mean(user_sys_time),
            sem_time = sd(user_sys_time)/sqrt(n),
            min = mean_time - sem_time,
            max = mean_time + sem_time) %>% 
  ungroup() %>% 
  ggplot(aes(x = fcov, y = mean_time, color=tool, group = tool)) +
  geom_point()  +
  geom_line() +
  geom_linerange(aes(ymin = min, ymax = max)) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  xlab("Fold coverage") +
  ylab("Runtime (s)") +
  scale_y_log10()

#print(coverage + theme(legend.position = "bottom"))

legend <- cowplot::get_legend(coverage + theme(legend.position = "bottom"))

figure_3 <- cowplot::plot_grid(coverage, viral_load, labels="AUTO")
figure_3 <- cowplot::plot_grid(figure_3, legend, ncol=1, rel_heights = c(1, 0.05))
print(figure_3)

cowplot::save_plot("plots/figure5_usr_plus_sys.pdf", figure_3)

```


```{r}
tool_order <- c("isling", "Polyidus", "Seeksv", "ViFi", "VSeq-Toolkit")

viral_load <- times %>% 
  filter(experiment == "viral_load") %>% 
  mutate(int_num = as_factor(int_num)) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  group_by(int_num, epi_num, tool) %>% 
  summarise(n = n(),
            mean_time = mean(duration_elapsed_time),
            sem_time = sd(duration_elapsed_time)/sqrt(n),
            min = mean_time - sem_time,
            max = mean_time + sem_time) %>% 
  ungroup() %>% 
   ggplot(aes(x = int_num, y = mean_time, color=tool, group = tool)) +
  geom_point()  +
  geom_line() +
  geom_linerange(aes(ymin = min, ymax = max)) +
  facet_wrap(vars(epi_num)) +
  theme_classic()  + 
  theme(
    strip.background = element_blank(),
    strip.text.y = element_blank(),
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    #    axis.title.y = element_blank(),
  )  +
  xlab("Number of integrations") +
  ylab("Runtime (s)") +
  scale_y_log10()


#print(viral_load + theme(legend.position = "bottom"))

coverage <- times %>% 
  filter(experiment == "coverage") %>% 
  mutate(fcov = as.factor(fcov)) %>% 
  mutate(tool = as.factor(tool)) %>% 
  mutate(tool = forcats::fct_relevel(tool, tool_order)) %>% 
  group_by(fcov, tool) %>% 
  summarise(n = n(),
            mean_time = mean(duration_elapsed_time),
            sem_time = sd(duration_elapsed_time)/sqrt(n),
            min = mean_time - sem_time,
            max = mean_time + sem_time) %>% 
  ungroup() %>% 
  ggplot(aes(x = fcov, y = mean_time, color=tool, group = tool)) +
  geom_point()  +
  geom_line() +
  geom_linerange(aes(ymin = min, ymax = max)) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  xlab("Fold coverage") +
  ylab("Runtime (s)") +
  scale_y_log10()

#print(coverage + theme(legend.position = "bottom"))

legend <- cowplot::get_legend(coverage + theme(legend.position = "bottom"))

figure_3 <- cowplot::plot_grid(coverage, viral_load, labels="AUTO")
figure_3 <- cowplot::plot_grid(figure_3, legend, ncol=1, rel_heights = c(1, 0.05))
print(figure_3)

cowplot::save_plot("plots/figure5_elapsed.pdf", figure_3)

```

```{r}
times %>% 
  group_by(dataset, int_num, fcov, epi_num, tool) %>% 
    summarise(n = n(),
            mean_time = mean(duration_elapsed_time),
            sem_time = sd(duration_elapsed_time)/sqrt(n),
            ) %>% 
  write_tsv("tables/runtimes.tsv")
```

