---
title: "Results for publication"
output: 
  html_notebook:
    code_folding: hide
---


```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(kableExtra)
library(cowplot)

source("sim_functions.R")

results_dir <- "../out/experiment1_OTC_chr1"
```

```{css, include=FALSE}
.scroll_100 {
  max-height: 300px;
  overflow-y: auto;
  background-color: inherit;
}
```


# Overview
I conducted several experiments in order to investigate the performatce of the pipeline, and compare it to similar tools.

## 'Easier' and 'harder'

The first experiment simulated some 'easier' and some 'harder' conditions.  I also tried out some wild-type virus (AAV2) and vector (OTC vector).

### Data
The only data required for simulation experiments are host and virus references.  

For the host, I used chromosome 1 from hg38.   

For the virus I used the OTC vector genome (the subsequence of the plasmid from ITR to ITR)

###  Easier and harder

I simulated two different situations using this data: one that I thought would be 'easier' for the pipeline to handle, and one that is 'harder'.

These conditions are summarised in the config file:

```{bash attr.output='style="max-height: 300px;"'}
cat ../config/experiment1_OTC_chr1/easier-harder.yml
```


#### Comparison with other tools

We can compare the performance of our pipeline with other tools

For each replicate, we can calulate the positive predictive value (how many of the predicted positves are true positves - high means few false positves), and the true positve rate (how many of the real positves are detected - high means few false negatives).


We can calculate the true positive rate (sensitivity, recall) as
$$TPR = \frac{TP}{P} = \frac{TP}{TP+FN}$$

And the positive predictive value as
$$PPV = \frac{TP}{TP+FP}$$

```{r include=FALSE}
exp_dir <- file.path(results_dir, "easier-harder")
int_scores <- importIntScoreExperiment(exp_dir) 

# only use postprocessed data from our pipeline
int_scores <- int_scores %>% 
  filter(case_when((analysis_tool != "pipeline") ~ TRUE,
                    post ~ TRUE,
                    TRUE ~ FALSE
    )) %>% 
  mutate(analysis_tool = str_replace(analysis_tool, 'analysis', 'isling')) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))
```

First, a table of results:
```{r}
int_scores %>% 
  select(experiment, replicate, window, coords_score_type, analysis_condition, TPR, PPV, tp:fn, results_file) %>% 
  arrange(experiment, analysis_condition, replicate, window) 
```

And also, a plot:
```{r}
for (i in unique(int_scores$window)) {
p <- int_scores %>% 
  filter(window == i) %>% 
  ggplot(aes(x = PPV, y = TPR, color = analysis_condition, shape = coords_score_type)) +
  geom_point() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_grid(vars(experiment), vars(coords_score_type)) +
  theme_bw() +
  ggtitle(i)
print(p)
}
```

If we just pick the score_type 'coords_mean' and distance 5, then we get:
```{r}
p <- int_scores %>% 
  filter(coords_score_type == "coords_mean") %>% 
  filter(window == 5) %>% 
  ggplot(aes(x = PPV, y = TPR, color = analysis_condition)) +
  geom_point() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(experiment)) +
  theme_classic() +
  theme(
    strip.background = element_rect(
      color = 'white', fill = "#f2f2f2", linetype = NULL
    )
  )
print(p)
```

```{r}
int_scores %>% 
  select(analysis_condition, merge, merge_dist, merge_n_min) %>% 
  distinct()
```

If we stick with analysis condition 2 (unmerged reads) for isling, and only show the 'harder' conditions:

```{r}
p <- int_scores %>% 
  filter(coords_score_type == "coords_mean") %>% 
  filter(ifelse(str_detect(analysis_condition, "isling"), str_detect(analysis_condition, "isling2"), TRUE)) %>% 
  filter(str_detect(experiment, "harder")) %>% 
  mutate(experiment = str_match("AAV|OTC", experiment)[,1]) %>% 
  ggplot(aes(x = PPV, y = TPR, color = analysis_condition)) +
  geom_point() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(experiment)) +
  theme_classic() +
  theme(
    strip.background = element_rect(
      color = 'white', fill = "#f2f2f2", linetype = NULL
        )
      ) +
  theme(legend.position="bottom")
print(p)
```




#### Distances from each found integration to the nearest simulated integration

We can also look at each output integration and check the distance to the nearest simulated integration.  

```{r include=FALSE}
found_scores <- importNearestSimToFound(exp_dir) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))
```

We expect all integrations to be on chromosomes 1, since this was the only chromosome used for simulation.  Plot the number of integrations on chromosome 1 and other chromosomes, in each condition.


```{r}
found_scores %>% 
  filter(ifelse(str_detect(analysis_condition, "isling"), str_detect(analysis_condition, "isling2"), TRUE)) %>% 
  mutate(dist = dist+1) %>% 
  ggplot(aes(x = dist, color = analysis_condition)) +
  geom_freqpoly(bins = 1000) +
  facet_grid(vars(experiment), vars(score_type), scales = 'free') +
  scale_x_log10()  +
  theme_classic() +
  theme(
    strip.background = element_rect(
      color = 'white', fill = "#f2f2f2", linetype = NULL
        )
      ) +
  theme(legend.position="bottom")
```

Plotting only the 'coords_mean' score type:

```{r}
found_scores %>% 
  filter(score_type == 'coords_mean') %>% 
  mutate(dist = dist+0.01) %>% 
  ggplot(aes(x = dist, color = analysis_condition)) +
  geom_freqpoly(bins = 1000) +
  facet_grid(vars(experiment), vars(analysis_condition), scales = 'free_y') +
  scale_x_log10() +
  theme(axis.text.x = element_text(angle = 90))  +
  theme_classic() +
  theme(
    strip.background = element_rect(
      color = 'white', fill = "#f2f2f2", linetype = NULL
        )
      ) +
  theme(legend.position="bottom")
```

Plotting only 'isling2' condition




#### Distances from each found integration to the nearest simulated integration

We can also look at each output integration and check the distance to the nearest simulated integration.  

```{r include=FALSE}
sim_scores <- importNearestFoundToSim(exp_dir) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))
```



```{r}
sim_scores %>% 
  filter(ifelse(str_detect(analysis_condition, "isling"), str_detect(analysis_condition, "isling2"), TRUE)) %>% 
  mutate(case_when(
    str_detect(analysis_condition, "isling") ~ "isling",
    TRUE ~ analysis_condition
  )) %>% 
  filter(score_type == "coords_mean") %>% 
  filter(score_dist == 5) %>% 
  mutate(dist = dist+1) %>% 
  ggplot(aes(x = dist, color = analysis_condition)) +
  geom_freqpoly(bins = 1000) +
  facet_grid(vars(experiment), vars(score_type), scales = 'free') +
  scale_x_log10()  +
  theme_classic() +
  theme(
    strip.background = element_rect(color = 'white', fill = "#f2f2f2", linetype = NULL)
      ) +
  theme(legend.position="bottom")
```




# Figure 1

```{r include=FALSE}
# import scored integrations
exp_dir <- file.path(results_dir, "easier-harder")
int_scores <- importIntScoreExperiment(exp_dir) 

# only use postprocessed data from our pipeline
int_scores <- int_scores %>% 
  filter(case_when((analysis_tool != "pipeline") ~ TRUE,
                    post ~ TRUE,
                    TRUE ~ FALSE
    )) %>% 
  mutate(analysis_tool = str_replace(analysis_tool, 'analysis', 'isling')) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))

#import distances from each found integration to nearest simulated integration
found_scores <- importNearestSimToFound(exp_dir) 

# only use postprocessed data from our pipeline
found_scores <- found_scores %>% 
  filter(case_when(
      !str_detect(analysis_condition, "pipeline") ~ TRUE,
      post ~ TRUE,
      TRUE ~ FALSE
    )) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))

# import distances from each simulated integration to the nearest found integration
sim_scores <- importNearestFoundToSim(exp_dir) 

sim_scores <- sim_scores%>% 
  filter(case_when(
      !str_detect(analysis_condition, "pipeline") ~ TRUE,
      post ~ TRUE,
      TRUE ~ FALSE
    )) %>%  
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))

```

Note that each integration has a left and right junction, so when scoring purely on host coordinates, each integration appears twice.  If there is a deletion from the host at the integration site, these two junctions will not be the in the same place in the host, otherwise they will be in the same place.


Note that when considering each found integration and looking for the nearest simulated integration, eac

```{r}
# filter data for plotting
isling_to_keep <- "isling2"

plot_found_scores <- found_scores %>% 
  filter(score_type == "coords_mean") %>% 
  filter(experiment == "OTC-harder" | experiment == "AAV-harder") %>% 
  filter(score_dist == 5) %>% 
  filter(ifelse(str_detect(analysis_condition, "isling"), str_detect(analysis_condition, isling_to_keep), TRUE)) %>%  # keep isling2 only
  mutate(tool = str_match(analysis_condition, "(.+)\\d+")[,2])
  

 
# double check filtering
plot_found_scores %>% 
  group_by(experiment, tool, score_dist, score_type, condition, replicate) %>% 
  summarise(tp = sum(score == "tp"),
            fp = sum(score == "fp"))

plot_sim_scores <- sim_scores %>% 
  filter(score_type == "coords_mean") %>% 
  filter(experiment == "OTC-harder" | experiment == "AAV-harder") %>% 
  filter(score_dist == 5) %>% 
  filter(ifelse(str_detect(analysis_condition, "isling"), str_detect(analysis_condition, isling_to_keep), TRUE)) %>%   # keep isling2 only
  mutate(tool = str_match(analysis_condition, "(.+)\\d+")[,2])

# double check filtering
plot_sim_scores %>% 
  group_by(experiment, tool, score_dist, score_type, condition, replicate) %>% 
  summarise(tp = sum(score == "tp"),
            fn = sum(score == "fn"),
            total_with_reads = n())

# scored integrations
plot_int_scores <- int_scores %>% 
  filter(coords_score_type == "coords_mean") %>% 
  filter(experiment == "OTC-harder" | experiment == "AAV-harder") %>% 
  filter(window == 5) %>% 
  filter(ifelse(str_detect(analysis_condition, "isling"), str_detect(analysis_condition, isling_to_keep), TRUE))
  
plot_int_scores %>% 
  select(experiment, analysis_tool, window, coords_score_type, condition, replicate, tp, fp, fn, PPV, TPR)

```


```{r}
# https://stackoverflow.com/questions/11335836/increase-number-of-axis-ticks
offset <- 0.5
num_y_breaks <- 2

OTC_found <- plot_found_scores %>% 
  filter(experiment == "OTC-harder") %>% 
  mutate(dist = dist+offset) %>% 
  ggplot(aes(x = dist, colour = tool)) +
  geom_freqpoly(bins = 20, show.legend = FALSE) +
  scale_x_log10() +
  facet_grid(rows = vars(tool), scales = "free_y") +
  xlab("Distance") +
  ylab("Count") +
  theme_classic()  + 
theme(
  strip.text.x = element_blank(),
  strip.text.y = element_blank(),
  strip.background = element_blank()
) +
scale_y_continuous(breaks = scales::pretty_breaks(n = num_y_breaks))


OTC_sim <- plot_sim_scores %>% 
  filter(experiment == "OTC-harder") %>% 
  mutate(dist = dist+offset) %>% 
  ggplot(aes(x = dist, colour = tool)) +
  geom_freqpoly(bins = 100, show.legend = FALSE) +
  scale_x_log10() +
  facet_grid(rows = vars(tool), scales = "free_y") +
  xlab("Distance") +
  ylab("Count") +
  theme_classic()  + 
theme(
  strip.background = element_blank(),
  strip.text.x = element_blank(),
  strip.text.y = element_blank(),
) +
scale_y_continuous(breaks = scales::pretty_breaks(n = num_y_breaks))


OTC_scores <- plot_int_scores %>% 
  filter(experiment == "OTC-harder") %>% 
  ggplot(aes(x = PPV, y = TPR, colour = analysis_tool)) +
  geom_point(show.legend = FALSE, alpha = 0.5) +
  xlim(0, 1) +
  ylim(0, 1) +
  xlab("Positive predictive value") +
  ylab("True positive rate") +
  theme_classic()


AAV_found <- plot_found_scores %>% 
  filter(experiment == "AAV-harder") %>% 
  mutate(dist = dist+offset) %>% 
  ggplot(aes(x = dist, colour = tool)) +
  geom_freqpoly(bins = 30, show.legend = FALSE) +
  scale_x_log10() +
  facet_grid(rows = vars(tool), scales = "free_y") +
  xlab("Distance") +
  ylab("Count") +
  theme_classic()  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()
)  +
scale_y_continuous(breaks = scales::pretty_breaks(n = num_y_breaks)) 


AAV_sim <- plot_sim_scores %>% 
  filter(experiment == "AAV-harder") %>% 
  mutate(dist = dist+offset) %>% 
  ggplot(aes(x = dist, colour = tool)) +
  geom_freqpoly(bins = 100, show.legend = FALSE) +
  scale_x_log10() +
  facet_grid(rows = vars(tool), scales = "free_y") +
  xlab("Distance") +
  ylab("Count") +
  theme_classic() + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(),
)  +
scale_y_continuous(breaks = scales::pretty_breaks(n = num_y_breaks))

AAV_scores <- plot_int_scores %>% 
  filter(experiment == "AAV-harder") %>% 
  ggplot(aes(x = PPV, y = TPR, colour = analysis_tool)) +
  geom_point(show.legend = FALSE, alpha = 0.5) +
  xlim(0, 1) +
  ylim(0, 1) +
  xlab("Positive predictive value") +
  ylab("True positive rate") +
  theme_classic()

dir.create("plots")
figure_1 <- cowplot::plot_grid(AAV_found, AAV_sim, AAV_scores, OTC_found, OTC_sim, OTC_scores, labels = "auto")
print(figure_1)
cowplot::save_plot("plots/figure_1.pdf", figure_1)


```
a, b, c : AAV_harder
d, e, f: OTC_harder
a, d: distance from each output integration to nearest simulated integration
b, e: distance from each simulated integration to nearest output integration
c, f: PPV and TPR with cutoff for distance = 5 (n = 3)
red - isling, green - polyidus, blue - seeksv, purple - vifi

###  Chromosomes

I also explored the effect of using different chromosomes as references for integraion.  I always used hg38 for analysis: see config file below:

```{bash attr.output='style="max-height: 300px;"'}
cat ../config/experiment1_OTC_chr1/chromosomes.yml
```

```{r include=FALSE}
exp_dir <- file.path(results_dir, "chromosomes")
int_scores <- importIntScoreExperiment(exp_dir) 


# only use postprocessed data from our pipeline
int_scores <- int_scores %>% 
  filter(case_when((analysis_tool != "pipeline") ~ TRUE,
                    post ~ TRUE,
                    TRUE ~ FALSE
    )) 
```

#### Scores

The results for these experiments:
```{r}
int_scores %>% 
  select(experiment, replicate, host_name, coords_score_type, analysis_tool, window, TPR, PPV, tp:fn) %>% 
  arrange(experiment, analysis_tool, replicate, host_name, window) 
```

```{r}
for (chr in unique(int_scores$host_name)) {
p <- int_scores %>% 
  filter(host_name == chr) %>% 
  ggplot(aes(x = PPV, y = TPR, color = analysis_tool)) +
  geom_point() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_grid(vars(experiment), vars(coords_score_type)) + 
  ggtitle(chr)
print(p)
}
```

```{r include=FALSE}
found_scores <- importNearestSimToFound(exp_dir) %>% 
  mutate(analysis_condition = str_replace(analysis_condition, 'analysis', 'isling'))

sim_conds <- importSimulationConditions(exp_dir)

found_scores <- left_join(found_scores, sim_conds, by=c("experiment", "condition", "replicate"))
```

What about the distance to the nearest simulated integration for every output integration?  When we combine all the chromosomes together:
```{r}
found_scores %>% 
  mutate(dist = dist+1) %>% 
  ggplot(aes(x = dist, color = analysis_condition)) +
  geom_freqpoly(bins = 1000) +
  facet_grid(vars(experiment), vars(score_type), scales = 'free') +
  scale_x_log10()
```

```{r}
found_scores %>% 
  filter(score_type == 'coords_mean') %>% 
  mutate(dist = dist+1) %>% 
  ggplot(aes(x = dist, color = analysis_condition)) +
  geom_freqpoly(bins = 1000) +
  facet_grid(vars(experiment), vars(host_name), scales = 'free_y') +
  scale_x_log10() +
  theme(axis.text.x = element_text(angle = 90))
```
### Simulation parameters - integration properties

I also explored the effect kinds of integrations: see config file below:

```{bash attr.output='style="max-height: 300px;"'}
cat ../config/experiment1_OTC_chr1/condition-breakdown.yml
```



```{r include=FALSE}
exp_dir <- file.path(results_dir, "condition-breakdown")
int_scores <- importIntScoreExperiment(exp_dir) 


# only use postprocessed data from our pipeline
int_scores <- int_scores %>% 
  filter(case_when((analysis_tool != "pipeline") ~ TRUE,
                    post ~ TRUE,
                    TRUE ~ FALSE
    ))  
```


```{r}
int_scores %>% 
  select(experiment, condition, replicate, post, analysis_tool, window, TPR, PPV, tp:fn) %>% 
  arrange(experiment, analysis_tool, condition, replicate,  window) 
```

The experiments completed so far are:
```{r}
unique(int_scores$experiment)
```

### Proportion of integrations with deletions
```{r}
int_scores %>% 
  filter(experiment == "OTC-deletion") %>% 
  group_by(condition, experiment, tool, window, p_delete) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = p_delete, y = PPV, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(window))
```


```{r}
int_scores %>% 
  filter(experiment == "OTC-deletion") %>% 
  group_by(condition, experiment, tool, window, p_delete) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = p_delete, y = TPR, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(window))
```

```{r}
int_scores %>% 
  filter(experiment == "OTC-fcov") %>% 
  ggplot(aes(x = PPV, y = TPR, color = tool, shape=as.factor(fcov))) +
  geom_point(alpha = 0.5) +
  facet_wrap(vars(window))
```


### Proportion of integrations with rearrangements
```{r}
int_scores %>% 
  filter(experiment == "OTC-rearrange") %>% 
  group_by(condition, experiment, tool, window, p_rearrange) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = p_rearrange, y = PPV, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(window))
```

```{r}
int_scores %>% 
  filter(experiment == "OTC-rearrange") %>% 
  group_by(condition, experiment, tool, window, p_rearrange) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = p_rearrange, y = TPR, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(window))
```

### Proportion of integrations that are whole
```{r}
int_scores %>% 
  filter(experiment == "OTC-whole") %>% 
  group_by(condition, experiment, tool, window, p_whole) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = p_whole, y = PPV, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(window))
```
```{r}
int_scores %>% 
  filter(experiment == "OTC-whole") %>% 
  group_by(condition, experiment, tool, window, p_whole) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = p_whole, y = TPR, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  xlim(0, 1) +
  ylim(0, 1) +
  facet_wrap(vars(window))
```

### Minimum length of integrations
```{r}
int_scores %>% 
  filter(experiment == "OTC-min_len") %>% 
  group_by(condition, experiment, tool, window, min_len) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = min_len, y = PPV, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  facet_wrap(vars(window))  + 
  ylim(0, 1) 
```

```{r}
int_scores %>% 
  filter(experiment == "OTC-min_len") %>% 
  group_by(condition, experiment, tool, window, min_len) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = min_len, y = TPR, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  facet_wrap(vars(window))  + 
  ylim(0, 1) 
```

### Minimum separation of integrations
```{r}
int_scores %>% 
  filter(experiment == "OTC-min_sep") %>% 
  group_by(condition, experiment, tool, window, min_sep) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = min_sep, y = PPV, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  facet_wrap(vars(window))  + 
  ylim(0, 1) 
```

```{r}
int_scores %>% 
  filter(experiment == "OTC-min_sep") %>% 
  group_by(condition, experiment, tool, window, min_sep) %>% 
  summarise(TPR = mean(TPR),
            TPR_sd = sd(TPR),
            PPV = mean(PPV),
            PPV_sd = sd(PPV),
            n= n()) %>% 
  ggplot(aes(x = min_sep, y = TPR, color = tool)) +
  geom_point(alpha = 0.5) +
  geom_line() +
  facet_wrap(vars(window))  + 
  ylim(0, 1) 
```

```{r}
sessionInfo()
```

